\chapter{Conclusion}

%STEPH MAKES IT

%Look at the PDF, it looks terrible. There are multiple paragraphs with 2-3 sentences only. I will rewrite the conclusion. - Bryan

%purpose of report, also quickly summarise previous (20 conc)
The aim of this report was to continue the design process and select one concept out of the five concepts that were found in the baseline report \cite{baseline}. These five were selected from a larger amount of concepts that also contained some unfeasible ideas. The five concepts were explained, using both text and sketches of the preliminary configuration for clarity. The concepts that were compared in this report are the Tailsitter, The Tandem, the Prandtl Box, the Tiltrotor, and the Winged Quadcopter.

%preliminary analysis of each of 5 concepts
The final concept was selected based on the score achieved in the final trade off. A preliminary analysis was performed on each of these concepts. It consisted of an assessment of the cost, development risk, flight performance, reliability, manoeuvrability, stability, ground handling, and sustainability. %check this
It was found that overall, the Winged Quadcopter performed best. 
%quickly summarise conclusions from each criterion
For the different criteria, some concepts stood out while others clearly under performed. 


%discuss all sections that are not part of the prel analysis
Besides performing the trade-off, some other aspects of the design process were analysed. A sensitivity analysis was performed, that showed in what way the trade-off would be affected when certain parameters would change.


A risk analysis was made, where the risk of not meeting any of the requirements was identified. It was found that for each concept, all risks that were present could be mitigated. 


A plan was made for the verification and validation steps that will be taken in the next design stage. The actual verification and validation will be presented in the final report.


Since sustainability is an important feature for the team, a plan was also made for sustainable development. It was decided to use Life Cycle Assessment as a guideline for the sustainable development of the design.

%summarise conclusion????
In the end, the Winged Quadcopter is the concept that will be taken along to the next design stage. A more elaborated analysis will be made of the concept, and a preliminary design will be presented in the final report.


%reccomendations

In the next stage of the project, the team will spend more time on verification and validation. It will also try to make more use of contact with companies that make hybrid UAVs, since it was found that the gathering of information on the subject is very difficult and not widely available.










